---
title: "Environmental filtering and habitat (mis)matching of riverine invertebrate communities"
subtitle: "NRSA DisEQ-Figures"
output:
  pdf_document:
    toc: true
    toc_depth: 4
    fig_caption: yes
    latex_engine: xelatex
always_allow_html: true
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
knitr::opts_chunk$set(results = "hold", fig.pos = "H", fig.align = "center", out.width = "92.5%")
options(knitr.graphics.error = FALSE)
kableExtra::usepackage_latex("float")
```

```{r Load Package for R Markdown, include = FALSE}
library(kableExtra)
library(knitr)
```

```{r Load Packages & Data, echo = TRUE}
## Load the tidyverse
library(tidyverse)
library(reshape2)

## Load vegan for the ordination
library(vegan)

## Packages for figures
library(ggpubr)
library(grid)
library(gridExtra)
library(scales)
library(viridis)
library(viridisLite)

## Packages for the site map
library(ggsn)
library(mapdata)
library(rgdal)

## Load the reduced workspace
load("data_analysis/2-DisEQ_analyses/2-DisEQ_analyses-Reduced_Workspace.RData")
```

```{r Set X-Axis Order, echo = TRUE}
## Reorder trait variables for plotting
trait.axis.limits <- c(
	"dispersal.low", "dispersal.high", 
	"flying.strength.none", "flying.strength.weak", "flying.strength.strong",
	"size.small", "size.medium", "size.large",
	"depositional", "depositional.erosional", "erosional",
	"cold", "cool.warm", "warm",
	"sensitive", "medium", "tolerant",
	"CG", "CF", "HB", "PR"
)

## Rename trait variables for plotting
trait.axis.labels <- c(
	"dispersal.low" = "Low Dispersal", "dispersal.high" = "High Dispersal", 
	"flying.strength.none" = "Nonflyer", "flying.strength.weak" = "Weak Flyer", 
	"flying.strength.strong" = "Strong Flyer",
	"size.small" = "Small Size", "size.medium" = "Medium Size", "size.large" = "Large Size",
	"depositional" = "Depositional", "depositional.erosional" = "Depo-Eros", "erosional" = "Erosional",
	"cold" = "Cold", "cool.warm" = "Cool-Warm", "warm" = "Warm",
	"sensitive" = "Sensitive", "medium" = "Intermediate", "tolerant" = "Tolerant",
	"CG" = "CG", "CF" = "CF", "HB" = "HB", "PR" = "PR"
)
```



\newpage
# Site Map

```{r Site Map, echo = TRUE}
## Figure was created by evaluating the supplementary R code and data
## provided by King et al. 2019 (Ecological Applications), deposited by
## Katelyn King on Zenodo at:

# https://zenodo.org/record/3246537#.XgDUKRdKhSw


## Set base projection and site locations
usa <- map_data("usa")  # pull out the USA map
base.map <- ggplot(data = usa) + 
	geom_polygon(aes(x = long, y = lat, group = group), 
							 fill = "white", color = "black") + 
	coord_fixed(1.3) 
points <- select(final.data, site.long, site.lat, ecoregion)

## Add points to the US map
site.map <- base.map +
	geom_point(data = points, size = 2, 
						 aes(x = site.long, y = site.lat, colour = ecoregion, shape = ecoregion)) +
	scale_colour_manual(values = viridis(n = 9), name = "Ecoregion") + 
	scale_shape_manual(values = c(0:8),  name = "Ecoregion") +
	north(data = usa, symbol = 3, scale = 0.1, location = "bottomright", 
				anchor = c(x = -120, y = 27)) +
	ggsn::scalebar(data = usa, dist = 500, dist_unit = "km", transform = TRUE, model = "WGS84", 
								 st.size = 2, location = "bottomleft") +
	theme(panel.grid.major = element_blank(), 
				panel.grid.minor = element_blank(),
				axis.line.x = element_blank(), 
				axis.title.x = element_blank(),
				axis.ticks.x = element_blank(),
				axis.text.x = element_blank(),
				axis.line.y = element_blank(), 
				axis.title.y = element_blank(),
				axis.ticks.y = element_blank(),
				axis.text.y = element_blank(),
				panel.background = element_blank()) +
	theme(legend.position = c(0.88, 0.20), legend.text = element_text(size = 9)) +
	theme(legend.text = element_text(size = 9))
```

```{r Save the Site Map, include = FALSE}
ggsave("Figure_1-site_map.jpg", 
			 plot = site.map, 
			 device = "jpg",
			 path = "figures/",
			 width = 12, 
			 height = 12,
			 units = "in", 
			 dpi = 1000
			 )
```

```{r View the Site Map, echo = FALSE, fig.cap = "Map of all 1078 sites included in the study."}
knitr::include_graphics(paste0(getwd(), "/figures/Figure_1-site_map.jpg"))
```



\newpage
# Filtering & Niche Mismatch ANOVAs

```{r Filtering & Niche Mismatch Data Management, echo = TRUE}
## Filtering and niche mismatch data management for plotting
DisEQ.data.wide <- final.DisEQ.data %>%
	select(UID, ecoregion, filtering.scaled, mismatch.scaled)

DisEQ.data.long <- DisEQ.data.wide %>%
	gather(DisEQ.metric, measurement, filtering.scaled:mismatch.scaled, factor_key = TRUE) %>%
	na.omit
```

```{r Filtering & Niche Mismatch, echo = TRUE}
DisEQ.figure <- ggerrorplot(
	data = DisEQ.data.long,
	x = "ecoregion",
	y = "measurement",
	size = 1.25, 
	width = 1.5,
	desc_stat = "mean",
	color = "ecoregion",
	xlab = "Ecoregion",
	ylab = "Measurement",
	title = "DisEQ by Ecoregion",
	palette = viridis(n = 9),
	add = "boxplot",
	ggtheme = theme_pubr(),
	legend = "right"
) %>%
	facet(
		facet.by = "DisEQ.metric",
		nrow = 2,
		ncol = 1,
		scales = "free_y"
	) +
	scale_x_discrete(limits = c("WMT", "XER", "NPL", "SPL", "TPL", "UMW", "NAP", "SAP", "CPL")) +
	geom_hline(yintercept = 0, linetype = 3, size = 1, colour = "gray20") +
	font("xlab", size = 16, color = "gray0") +
	font("ylab", size = 16, color = "gray0") +
	font("xy.text", size = 12, color = "gray20")
```

```{r Save the Filtering & Niche Mismatch Figure, include = FALSE}
## Export the figure
ggsave("Figure_2-filtering_mismatch_ANOVAs.jpg", 
			 plot = DisEQ.figure, 
			 device = "jpg",
			 path = "figures/",
			 width = 8, 
			 height = 6,
			 units = "in", 
			 dpi = 900)
```

\newpage
```{r View the Filtering & Niche Mismatch Figure, echo = FALSE, fig.cap = "Plots of environmental filtering and niche mismatch by ecoregion."}
knitr::include_graphics(paste0(getwd(), "/figures/Figure_2-filtering_mismatch_ANOVAs.jpg"))
```



\newpage
# Habitat Matching & Mismatch Vector Component ANOVAs

```{r Habitat Matching & Mismatch Vector Component Data Management, echo = TRUE}
## Vector component data management for plotting
vector.component.wide <- final.DisEQ.data %>%
	select(UID, ecoregion, Tmax.direction, Tmin.direction, pH.direction, cond.direction)

vector.component.long <- vector.component.wide %>%
	gather(vector.component, measurement, Tmax.direction:cond.direction, factor_key = TRUE) %>%
	na.omit
```

```{r Habitat Matching & Mismatch Vector Component Figure, echo = TRUE}
vector.component.figure <- ggerrorplot(
	data = vector.component.long,
	x = "ecoregion",
	y = "measurement",
	size = 1.25, 
	width = 1.5,
	desc_stat = "mean",
	color = "ecoregion",
	xlab = "Ecoregion",
	ylab = "Measurement",
	title = "Vector Component",
	palette = viridis(n = 9),
	add = "boxplot",
	ggtheme = theme_pubr(),
	legend = "right"
) %>%
	facet(
		facet.by = "vector.component",
		nrow = 2,
		ncol = 2,
		scales = "free_y"
	) +
	scale_x_discrete(limits = c("WMT", "XER", "NPL", "SPL", "TPL", "UMW", "NAP", "SAP", "CPL")) +
	font("xlab", size = 16, color = "gray0") +
	font("ylab", size = 16, color = "gray0") +
	font("xy.text", size = 12, color = "gray20")
```

```{r Save the Habitat Matching & Mismatch Vector Component Figure, include = FALSE}
## Export the figure
ggsave("Figure_S1-vector_components.jpg", 
			 plot = vector.component.figure, 
			 device = "jpg",
			 path = "figures/",
			 width = 10, 
			 height = 7.5,
			 units = "in", 
			 dpi = 900)
```

\newpage
```{r View the Matching & Mismatch Vector Component Figure, echo = FALSE, fig.cap = "Plots of vector components of habitat matching and mismatch."}
knitr::include_graphics(paste0(getwd(), "/figures/Figure_S1-vector_components.jpg"))
```



\newpage
# Functional Trait Diversity ANOVAs

```{r Trait Diversity Data Management, echo = TRUE}
## Trait diversity data management for plotting
trait.diversity.wide <- final.DisEQ.data %>%
	select(UID, ecoregion, FRic, FEve, FDiv, FDis)

trait.diversity.long <- trait.diversity.wide %>%
	gather(diversity.measure, measurement, FRic:FDis, factor_key = TRUE) %>%
	na.omit
```

```{r Trait Diversity Figure, echo = TRUE}
trait.diversity.figure <- ggerrorplot(
	data = trait.diversity.long,
	x = "ecoregion",
	y = "measurement",
	size = 1.25, 
	width = 1.5,
	desc_stat = "mean",
	color = "ecoregion",
	xlab = "Ecoregion",
	ylab = "Measurement",
	title = "Trait Diversity",
	palette = viridis(n = 9),
	add = "boxplot",
	ggtheme = theme_pubr(),
	legend = "right"
) %>%
	facet(
		facet.by = "diversity.measure",
		nrow = 2,
		ncol = 2,
		scales = "free_y"
	) +
	scale_x_discrete(limits = c("WMT", "XER", "NPL", "SPL", "TPL", "UMW", "NAP", "SAP", "CPL")) +
	font("xlab", size = 16, color = "gray0") +
	font("ylab", size = 16, color = "gray0") +
	font("xy.text", size = 12, color = "gray20")
```

```{r Save the Trait Diversity Figure, include = FALSE}
## Export the figure
ggsave("Figure_3-trait_diversity.jpg", 
			 plot = trait.diversity.figure, 
			 device = "jpg",
			 path = "figures/",
			 width = 10, 
			 height = 7.5,
			 units = "in", 
			 dpi = 900)
```

\newpage
```{r View the Trait Diversity Figure, echo = FALSE, fig.cap = "Plots of FRic, FEve, FDiv, and FDis by ecoregion."}
knitr::include_graphics(paste0(getwd(), "/figures/Figure_3-trait_diversity.jpg"))
```



\newpage
# DisEQ-by-Traits

## Filtering-by-Traits Figure

```{r Filtering-by-Traits Data Management, echo = TRUE}
## Re-order ecoregion for facet plots
filtering.by.trait.BRT.results$ecoregion <- factor(
	filtering.by.trait.BRT.results$ecoregion,
	levels = c("WMT", "UMW", "NAP", "XER", "NPL", "SAP", "SPL", "TPL", "CPL")
)
```

```{r Filtering-by-Traits Figure, echo = TRUE}
filtering.by.traits.figure <- ggbarplot(
	data = filtering.by.trait.BRT.results,
	x = "var",
	y = "rel.inf",
	fill = "predictor.type",
	xlab = "Trait",
	ylab = "Relative Influence",
	title = "Filtering by Traits",
	facet.by = "ecoregion",
	palette = plasma(n = 3),
	ggtheme = theme_pubr(),
	legend = "right"
) +
	scale_x_discrete(
		limits = trait.axis.limits,
		labels = trait.axis.labels
		) +
	scale_y_continuous(breaks = c(0, 5, 10), limits = c(0, 11.25)) +
	rotate_x_text(angle = 90) +
	font("xlab", size = 16, color = "gray0") +
	font("ylab", size = 16, color = "gray0") +
	font("xy.text", size = 12, color = "gray20")
```

```{r Save the Filtering-by-Traits Figure, include = FALSE}
## Export the figure
ggsave("Figure_4-filtering_by_traits.jpg", 
			 plot = filtering.by.traits.figure, 
			 device = "jpg",
			 path = "figures/",
			 width = 12, 
			 height = 12,
			 units = "in", 
			 dpi = 900)
```

\newpage
```{r View the Filtering-by-Traits Figure, echo = FALSE, fig.cap = "Plots of relative influence for each of 21 traits across ecoregions"}
knitr::include_graphics(paste0(getwd(), "/figures/Figure_4-filtering_by_traits.jpg"))
```


\newpage
## Mismatch-by-Traits Figure

```{r Mismatch-by-Traits Data Management, echo = TRUE}
## Re-order ecoregion for facet plots
mismatch.by.trait.BRT.results$ecoregion <- factor(
	mismatch.by.trait.BRT.results$ecoregion,
	levels = c("WMT", "UMW", "NAP", "XER", "NPL", "SAP", "SPL", "TPL", "CPL")
)
```

```{r Mismatch-by-Traits Figure, echo = TRUE}
mismatch.by.traits.figure <- ggbarplot(
	data = mismatch.by.trait.BRT.results,
	x = "var",
	y = "rel.inf",
	fill = "predictor.type",
	xlab = "Trait",
	ylab = "Relative Influence",
	title = "Habitat Matching by Traits",
	facet.by = "ecoregion",
	palette = plasma(n = 3),
	ggtheme = theme_pubr(),
	legend = "right"
) +
	scale_x_discrete(
		limits = trait.axis.limits,
		labels = trait.axis.labels) +
	rotate_x_text(angle = 90) +
	font("xlab", size = 16, color = "gray0") +
	font("ylab", size = 16, color = "gray0") +
	font("xy.text", size = 12, color = "gray20")
```

```{r Save the Mismatch-by-Traits Figure, include = FALSE}
## Export the figure
ggsave("Figure_5-mismatch_by_traits.jpg", 
			 plot = mismatch.by.traits.figure, 
			 device = "jpg",
			 path = "figures/",
			 width = 12, 
			 height = 12,
			 units = "in", 
			 dpi = 900)
```

\newpage
```{r View the Mismatch-by-Traits Figure, echo = FALSE, fig.cap = "Plots of relative influence by dispersal, ecology, and habitat traits for each of 21 traits across all 9 ecoregions"}
knitr::include_graphics(paste0(getwd(), "/figures/Figure_5-mismatch_by_traits.jpg"))
```



\newpage
# Traits-by-Environment

```{r Traits-by-Environment Data Management, echo = TRUE}
## Bind all BRT results into a long dataframe for plotting
trait.by.environment.long.bin.1 <- bind_rows(
	low.dispersal.environment.BRT.results, high.dispersal.environment.BRT.results,
	nonflyer.environment.BRT.results, weak.flyer.environment.BRT.results,
	strong.flyer.environment.BRT.results, small.size.environment.BRT.results,
	medium.size.environment.BRT.results, large.size.environment.BRT.results,
	depositional.environment.BRT.results, depositional.erosional.environment.BRT.results,
	erosional.environment.BRT.results, cold.water.environment.BRT.results,
	cool.warm.water.environment.BRT.results, warm.water.environment.BRT.results,
	sensitive.tolerance.environment.BRT.results, intermediate.tolerance.environment.BRT.results,
	tolerant.environment.BRT.results, CG.environment.BRT.results,
	CF.environment.BRT.results, HB.environment.BRT.results, PR.environment.BRT.results
)

## Add trait vector to the dataframe
trait.by.environment.long.bin.1$trait <- rep(
	c("Low Dispersal", "High Dispersal",
		"Nonflyer", "Weak Flyer", "Strong Flyer",
		"Small Size", "Medium Size", "Large Size",
		"Depositional", "Depo-Eros", "Erosional",
		"Cold", "Cool-Warm", "Warm",
		"Sensitive", "Intermediate", "Tolerant",
		"CG", "CF", "HB", "PR"),
	each = 162)

## Sum relative influence by predictor type and ecoregion for each trait
trait.by.environment.long <- aggregate(
	rel.inf ~ trait + ecoregion + predictor.type,
	data = trait.by.environment.long.bin.1,
	FUN = sum
)

## Re-order ecoregion for facet plots
trait.by.environment.long$ecoregion <- factor(
	trait.by.environment.long$ecoregion,
	levels = c("WMT", "UMW", "NAP", "XER", "NPL", "SAP", "SPL", "TPL", "CPL")
)
```

```{r Traits-by-Environment Figure, echo = TRUE}
traits.by.environment.figure <- ggbarplot(
	data = trait.by.environment.long,
	x = "trait",
	y = "rel.inf",
	fill = "predictor.type",
	color = "predictor.type",
	xlab = "Trait",
	ylab = "Relative Influence",
	title = "Traits by Environment",
	facet.by = "ecoregion",
	palette = viridis(n = 3),
	ggtheme = theme_pubr(),
	legend = "right"
) +
	scale_x_discrete(
		limits = 	c(
			"Low Dispersal", "High Dispersal", "Nonflyer", "Weak Flyer", "Strong Flyer",
			"Small Size", "Medium Size", "Large Size", "Depositional", "Depo-Eros", "Erosional",
			"Cold", "Cool-Warm", "Warm", "Sensitive", "Intermediate", "Tolerant",
			"CG", "CF", "HB", "PR"),
		labels = c(
			"Low Dispersal", "High Dispersal", "Nonflyer", "Weak Flyer", "Strong Flyer",
			"Small Size", "Medium Size", "Large Size", "Depositional", "Depo-Eros", "Erosional",
			"Cold", "Cool-Warm", "Warm", "Sensitive", "Intermediate", "Tolerant",
			"CG", "CF", "HB", "PR")
		) +
	rotate_x_text(angle = 90) +
	font("xlab", size = 16, color = "gray0") +
	font("ylab", size = 16, color = "gray0") +
	font("xy.text", size = 12, color = "gray20")
```

```{r Save the Traits-by-Environment Figure, include = FALSE}
## Export the figure
ggsave("Figure_6-traits_by_environment.jpg", 
			 plot = traits.by.environment.figure, 
			 device = "jpg",
			 path = "figures/",
			 width = 12, 
			 height = 12,
			 units = "in", 
			 dpi = 900)
```

\newpage
```{r View the Traits-by-Environment Figure, echo = FALSE, fig.cap = "Plots of relative influence by environmental, landscape, and network predictors for each of 21 traits across all 9 ecoregions"}
knitr::include_graphics(paste0(getwd(), "/figures/Figure_6-traits_by_environment.jpg"))
```



\newpage
# DisEQ & Functional Diversity ANCOVAs

```{r DisEQ & Trait Diversity: Data Management, echo = TRUE}
## DisEQ and trait diversity data management
# Wide format
DisEQ.trait.diversity.wide <- final.DisEQ.data %>%
	select(filtering.scaled, mismatch.scaled, ecoregion, FRic, FEve, FDiv, FDis)

# Switch from wide to long
DisEQ.trait.diversity.long <- DisEQ.trait.diversity.wide %>%
	gather(trait.metric, measurement, FRic:FDis, factor_key = TRUE) %>%
	na.omit
```


## Filtering by Functional Diversity

```{r DisEQ & Trait Diversity: Filtering Figure, echo = TRUE}
filtering.by.trait.diversity.figure <- ggscatter(
	data = DisEQ.trait.diversity.long,
	x = "measurement",
	y = "filtering.scaled",
	size = 1,
	color = "ecoregion",
	xlab = "Trait Diversity",
	ylab = "Environmental Filtering",
	title = "Environmental Filtering by Functional Diversity",
	palette = viridis(n = 9),
	ggtheme = theme_pubr(),
	legend = "right",
	add = "reg.line",
	conf.int = TRUE
) %>%
	facet(
		facet.by = "trait.metric",
		nrow = 2,
		ncol = 2,
		scales = "free"
	) +
	font("xlab", size = 16, color = "gray0") +
	font("ylab", size = 16, color = "gray0") +
	font("xy.text", size = 12, color = "gray20") +
	geom_hline(yintercept = 0, linetype = 3, size = 1, colour = "gray40")
```

```{r Save the Filtering by Functional Diversity Figure, include = FALSE}
## Export the figure
ggsave("Figure_S2-filtering_by_trait_diversity.jpg", 
			 plot = filtering.by.trait.diversity.figure, 
			 device = "jpg",
			 path = "figures/",
			 width = 12, 
			 height = 12,
			 units = "in", 
			 dpi = 900)
```


\newpage
## Habitat Matching by Functional Diversity

```{r DisEQ & Trait Diversity: Habitat Matching Figure, echo = TRUE}
mismatch.by.trait.diversity.figure <- ggscatter(
	data = DisEQ.trait.diversity.long,
	x = "measurement",
	y = "mismatch.scaled",
	size = 1,
	color = "ecoregion",
	xlab = "Trait Diversity",
	ylab = "Habitat Matching",
	title = "Habitat Matching by Functional Diversity",
	palette = viridis(n = 9),
	ggtheme = theme_pubr(),
	legend = "right",
	add = "reg.line",
	conf.int = TRUE
) %>%
	facet(
		facet.by = "trait.metric",
		nrow = 2,
		ncol = 2,
		scales = "free"
	) +
	font("xlab", size = 16, color = "gray0") +
	font("ylab", size = 16, color = "gray0") +
	font("xy.text", size = 12, color = "gray20") +
	geom_hline(yintercept = 0, linetype = 3, size = 1, colour = "gray40")
```

```{r Save the Habitat Matching by Functional Diversity Figure, include = FALSE}
## Export the figure
ggsave("Figure_S3-mismatch_by_trait_diversity.jpg", 
			 plot = mismatch.by.trait.diversity.figure, 
			 device = "jpg",
			 path = "figures/",
			 width = 12, 
			 height = 12,
			 units = "in", 
			 dpi = 900)
```


\newpage
```{r View the Filtering by Trait Diversity Figure, echo = FALSE, fig.cap = "Plots of environmental filtering against measures of functional trait diversity."}
knitr::include_graphics(paste0(getwd(), "/figures/Figure_S2-filtering_by_trait_diversity.jpg"))
```


\newpage
```{r View the Habitat Matching by Trait Diversity Figure, echo = FALSE, fig.cap = "Plots of habitat matching against measures of functional trait diversity."}
knitr::include_graphics(paste0(getwd(), "/figures/Figure_S3-mismatch_by_trait_diversity.jpg"))
```



\newpage
# Environmental Filtering & Habitat Matching Model

```{r DisEQ LMM Figure, echo = TRUE}
DisEQ.LMM.figure <- ggscatter(
	data = final.DisEQ.data,
	x = "mismatch.scaled",
	y = "filtering.scaled",
	size = 1,
	color = "ecoregion",
	xlab = "Habitat Matching",
	ylab = "Environmental Filtering",
	palette = viridis(n = 9),
	ggtheme = theme_pubr(),
	legend = "right",
	add = "reg.line",
	conf.int = TRUE
) +
	geom_hline(yintercept = 0, linetype = 3, size = 1, colour = "gray40") +
	geom_vline(xintercept = 0, linetype = 3, size = 1, colour = "gray40")
```

```{r Save the DisEQ LMM Figure, include = FALSE}
## Export the figure
ggsave("Figure_S4-DisEQ_regression.jpg", 
			 plot = DisEQ.LMM.figure, 
			 device = "jpg",
			 path = "figures/",
			 width = 12, 
			 height = 12,
			 units = "in", 
			 dpi = 900)
```

\newpage
```{r View the DisEQ LMM Figure, echo = FALSE, fig.cap = "Plot of environmental filtering against habitat matching while controlling for the effect of ecoregion."}
knitr::include_graphics(paste0(getwd(), "/figures/Figure_S4-DisEQ_regression.jpg"))
```



\newpage
# Community Composition

```{r Community Composition Figure, echo = TRUE, results = "hide"}
## Make panel figure
par(mfrow = c(1, 1), mar = c(5, 5, 5, 5))

## Create identifier
NMDS.groups <- final.data[rowSums(final.data[, 67:142]) > 0, 25]

## Set figure dimensions
pdf("figures/Figure_S5A-community_composition-base.pdf", width = 8, height = 6)

## NMDS plot (axes 1 and 2)
axes.1_2 <- ordiplot(BC.NMDS, choices = c(1, 2), type = "none", display = "sites",
										 xlim = c(-1.5, 1.5), ylim = c(-1.5, 1.5), xlab = "NMDS 1", ylab = "NMDS 2")
ordiellipse(BC.NMDS, groups = NMDS.groups, 
						draw = "lines", col = viridis(n = 9), label = FALSE, lwd = 5)
mtext(text = "Stress = 0.199", side = 3, line = -1.5, adj = 0.95, 
			cex = 1.05)
mtext(text = "(A)", side = 3, line = 1.75, adj = 0.05, cex = 1.25)
legend(1.75, 0.45, c("CPL", "NAP", "NPL", "SAP", "SPL", "TPL", "UMW", "WMT", "XER"),  
			 cex = 0.75, lty = 1, lwd = 4, x.intersp = 0.95, y.intersp = 0.95,
			 col = viridis(n = 9))
## Export the figure
dev.off()


## Set figure dimensions
pdf("figures/Figure_S5B-community_composition-base.pdf", width = 8, height = 6)

## NMDS plot (axes 1 and 3)
axes.1_3 <- ordiplot(BC.NMDS, choices = c(1, 3), type = "none", display = "sites",
										 xlim = c(-1.5, 1.5), ylim = c(-1.5, 1.5), xlab = "NMDS 1", ylab = "NMDS 3")
ordiellipse(axes.1_3, groups = NMDS.groups, 
						draw = "lines", col = viridis(n = 9), label = FALSE, lwd = 5)
mtext(text = "(B)", side = 3, line = 1.75, adj = 0.025, cex = 1.25)

## Export the figure
dev.off()
```

\newpage
```{r View the Community Composition Panel Figure, echo = FALSE, fig.cap = "Plot of community composition by ecoregion."}
knitr::include_graphics(paste0(getwd(), "/figures/Figure_S5-community_composition.jpg"))
```




\newpage
# R Session Information

```{r R Packages, echo = FALSE}
df_session_packages <- devtools::session_info()$packages %>% 
  as.data.frame(.) %>% 
  filter(attached == TRUE) %>% 
  dplyr::select(loadedversion, date) %>% 
  rownames_to_column

colnames(df_session_packages) <- c("Package", "Loaded Version", "Date")

kable(
  df_session_packages, 
  booktabs = TRUE,
  caption = "Packages required for data management and figure creation."
  ) %>%
	kable_styling(
		full_width = FALSE,
  	latex_options = c("HOLD_position", "striped")
  	) 
```

