---
title: "Environmental filtering and habitat (mis)matching of riverine invertebrate communities"
subtitle: "NRSA DisEQ-BRT Supplemental Tables"
output:
  pdf_document:
    fig_caption: yes
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
knitr::opts_chunk$set(results = "hold", fig.pos = "H", fig.align = "center", out.width = "92.5%")
options(knitr.graphics.error = FALSE)
kableExtra::usepackage_latex("float")
```

```{r Load Package for R Markdown, include = FALSE}
library(kableExtra)
library(knitr)
```

```{r Load Packages & Data, include = FALSE}
library(tidyverse)
library(reshape2)

## Load the reduced workspace
load("data_analysis/2-DisEQ_analyses/2-DisEQ_analyses-Reduced_Workspace.RData")
```


\newpage
# DisEQ-by-Traits

Supplementary tables for the DisEQ-by-traits boosted regression trees. Complete tables of the relative influence for each trait predictor are provided (Tables 1-2), along with tables presenting the summed relative influence for all predictor variables within the respective category with a relative influence >5.00 (Tables 3-4).


```{r DisEQ-by-Traits Data Mangement, include = FALSE}
## Format DisEQ-by-traits matrices for plotting

## Filtering by traits
filtering.by.traits.matrix <- dcast(
	filtering.by.trait.BRT.results, ecoregion ~ var, value.var = "rel.inf"
	) %>%
	select(c(9, 8, 11, 13, 12, 20, 19, 18, 6:7, 10, 4:5, 22, 17, 15, 21, 3, 2, 14, 16)) %>%
	as.matrix()

colnames(filtering.by.traits.matrix) <- c(
	"Low Dispersal", "High Dispersal", "Nonflyer", "Weak Flyer", "Strong Flyer",
	"Small Size", "Medium Size", "Large Size", "Depositional", "Depositional-Erosional", 
	"Erosional", "Cold Water", "Cool-Warm Water", "Warm Water",
	"Sensitive Tolerance", "Intermediate Tolerance", "Tolerant",
	"CG", "CF", "HB", "PR"
	)

rownames(filtering.by.traits.matrix) <- c(
	"CPL", "NAP", "NPL", "SAP", "SPL", "TPL", "UMW", "WMT", "XER"
)

## Mismatch by traits
mismatch.by.traits.matrix <- dcast(
	mismatch.by.trait.BRT.results, ecoregion ~ var, value.var = "rel.inf"
	) %>%
	select(c(9, 8, 11, 13, 12, 20, 19, 18, 6:7, 10, 4:5, 22, 17, 15, 21, 3, 2, 14, 16)) %>%
	as.matrix()

colnames(mismatch.by.traits.matrix) <- c(
	"Low Dispersal", "High Dispersal", "Nonflyer", "Weak Flyer", "Strong Flyer",
	"Small Size", "Medium Size", "Large Size", "Depositional", "Depositional-Erosional", 
	"Erosional", "Cold Water", "Cool-Warm Water", "Warm Water",
	"Sensitive Tolerance", "Intermediate Tolerance", "Tolerant",
	"CG", "CF", "HB", "PR"
	)

rownames(mismatch.by.traits.matrix) <- c(
	"CPL", "NAP", "NPL", "SAP", "SPL", "TPL", "UMW", "WMT", "XER"
)
```





```{r Filtering-by-Traits Relative Influence, echo = FALSE}
kable(
	filtering.by.traits.matrix,
	booktabs = TRUE,
	digits = 2,
	caption = "Table of relative influence values for trait predictors in the filtering-by-traits boosted regression trees, with relative influence values provided for each ecoregion."
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped", "scale_down")) %>%
	landscape()
```

```{r Mismatch-by-Traits Relative Influence, echo = FALSE}
kable(
	mismatch.by.traits.matrix,
	booktabs = TRUE,
	digits = 2,
	caption = "Table of relative influence values for trait predictors in the mismatch-by-traits boosted regression trees, with relative influence values provided for each ecoregion."
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped", "scale_down")) %>%
	landscape()
```





```{r Filtered DisEQ-by-Traits Results, include = FALSE}
## Filter data to only include variables with a relative influence >= 5.00

## Filtering-by-traits
filtering.by.trait.threshold.RI <- filtering.by.trait.BRT.results %>%
	filter(rel.inf > 5.00) %>%
	group_by(ecoregion, predictor.type) %>%
	summarise(summed.RI = sum(rel.inf))

## Mismatch-by-traits
mismatch.by.trait.threshold.RI <- mismatch.by.trait.BRT.results %>%
	filter(rel.inf > 5.00) %>%
	group_by(ecoregion, predictor.type) %>%
	summarise(summed.RI = sum(rel.inf))
```


```{r Filtering-by-Traits Summed Relative Influence, echo = FALSE}
kable(
	filtering.by.trait.threshold.RI,
	booktabs = TRUE,
	digits = 2,
	caption = "Summed relative influence for all predictor variables within the respective category with a relative influence >5.00 for the filtering-by-traits boosted regression trees. Summed relative influence was calculated for each of the ecoregions.",
	col.names = c("Ecoregion", "Predictor Category", "Relative Influence")
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{4pt}

```{r Mismatch-by-Traits Summed Relative Influence, echo = FALSE}
kable(
	mismatch.by.trait.threshold.RI,
	booktabs = TRUE,
	digits = 2,
	caption = "Summed relative influence for all predictor variables within the respective category with a relative influence >5.00 for the mismatch-by-traits boosted regression trees. Summed relative influence was calculated for each of the ecoregions.",
	col.names = c("Ecoregion", "Predictor Category", "Relative Influence")
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped"))
```


\newpage
# Trait-by-Environment

Supplementary tables for the trait-by-environment boosted regression trees. Complete tables of the relative influence for each trait predictor are provided (Tables 5-25), along with tables presenting the summed relative influence for all predictor variables within the respective category with a relative influence >5.00 (Tables 26-46).


```{r Traits-by-Environment Data Management, include = FALSE}
## Format traits-by-environment matrices for plotting

## Low dispersal
low.dispersal.by.environment.matrix <- dcast(
	low.dispersal.environment.BRT.results, ecoregion ~ var, value.var = "rel.inf"
	) %>%
	select(c(18:19, 5:6, 9, 2:3, 11, 10, 13, 12, 7, 17, 16, 4, 8, 14:15)) %>%
	as.matrix()

colnames(low.dispersal.by.environment.matrix) <- c(
	"Total N", "Total P", "DOC", "LWD Reach", "NAT Cover", "ALG Cover", "AQM Cover",
	"% Forested", "% Ag", "% Urban", "% ISC", "Mean Annual Flow", "Longitude", "Latitude",
	"Basin Area", "Mean Basin Elevation", "Range Basin Elevation", "Site Centrality"
	)

rownames(low.dispersal.by.environment.matrix) <- c(
	"CPL", "NAP", "NPL", "SAP", "SPL", "TPL", "UMW", "WMT", "XER"
)

## High dispersal
high.dispersal.by.environment.matrix <- dcast(
	high.dispersal.environment.BRT.results, ecoregion ~ var, value.var = "rel.inf"
	) %>%
	select(c(18:19, 5:6, 9, 2:3, 11, 10, 13, 12, 7, 17, 16, 4, 8, 14:15)) %>%
	as.matrix()

colnames(high.dispersal.by.environment.matrix) <- c(
	"Total N", "Total P", "DOC", "LWD Reach", "NAT Cover", "ALG Cover", "AQM Cover",
	"% Forested", "% Ag", "% Urban", "% ISC", "Mean Annual Flow", "Longitude", "Latitude",
	"Basin Area", "Mean Basin Elevation", "Range Basin Elevation", "Site Centrality"
	)

rownames(high.dispersal.by.environment.matrix) <- c(
	"CPL", "NAP", "NPL", "SAP", "SPL", "TPL", "UMW", "WMT", "XER"
)

## Nonflyer
nonflyer.by.environment.matrix <- dcast(
	nonflyer.environment.BRT.results, ecoregion ~ var, value.var = "rel.inf"
	) %>%
	select(c(18:19, 5:6, 9, 2:3, 11, 10, 13, 12, 7, 17, 16, 4, 8, 14:15)) %>%
	as.matrix()

colnames(nonflyer.by.environment.matrix) <- c(
	"Total N", "Total P", "DOC", "LWD Reach", "NAT Cover", "ALG Cover", "AQM Cover",
	"% Forested", "% Ag", "% Urban", "% ISC", "Mean Annual Flow", "Longitude", "Latitude",
	"Basin Area", "Mean Basin Elevation", "Range Basin Elevation", "Site Centrality"
	)

rownames(nonflyer.by.environment.matrix) <- c(
	"CPL", "NAP", "NPL", "SAP", "SPL", "TPL", "UMW", "WMT", "XER"
)

## Weak flyer
weak.flyer.by.environment.matrix <- dcast(
	weak.flyer.environment.BRT.results, ecoregion ~ var, value.var = "rel.inf"
	) %>%
	select(c(18:19, 5:6, 9, 2:3, 11, 10, 13, 12, 7, 17, 16, 4, 8, 14:15)) %>%
	as.matrix()

colnames(weak.flyer.by.environment.matrix) <- c(
	"Total N", "Total P", "DOC", "LWD Reach", "NAT Cover", "ALG Cover", "AQM Cover",
	"% Forested", "% Ag", "% Urban", "% ISC", "Mean Annual Flow", "Longitude", "Latitude",
	"Basin Area", "Mean Basin Elevation", "Range Basin Elevation", "Site Centrality"
	)

rownames(weak.flyer.by.environment.matrix) <- c(
	"CPL", "NAP", "NPL", "SAP", "SPL", "TPL", "UMW", "WMT", "XER"
)

## Strong flyer
strong.flyer.by.environment.matrix <- dcast(
	strong.flyer.environment.BRT.results, ecoregion ~ var, value.var = "rel.inf"
	) %>%
	select(c(18:19, 5:6, 9, 2:3, 11, 10, 13, 12, 7, 17, 16, 4, 8, 14:15)) %>%
	as.matrix()

colnames(strong.flyer.by.environment.matrix) <- c(
	"Total N", "Total P", "DOC", "LWD Reach", "NAT Cover", "ALG Cover", "AQM Cover",
	"% Forested", "% Ag", "% Urban", "% ISC", "Mean Annual Flow", "Longitude", "Latitude",
	"Basin Area", "Mean Basin Elevation", "Range Basin Elevation", "Site Centrality"
	)

rownames(strong.flyer.by.environment.matrix) <- c(
	"CPL", "NAP", "NPL", "SAP", "SPL", "TPL", "UMW", "WMT", "XER"
)

## Small size
small.size.by.environment.matrix <- dcast(
	small.size.environment.BRT.results, ecoregion ~ var, value.var = "rel.inf"
	) %>%
	select(c(18:19, 5:6, 9, 2:3, 11, 10, 13, 12, 7, 17, 16, 4, 8, 14:15)) %>%
	as.matrix()

colnames(small.size.by.environment.matrix) <- c(
	"Total N", "Total P", "DOC", "LWD Reach", "NAT Cover", "ALG Cover", "AQM Cover",
	"% Forested", "% Ag", "% Urban", "% ISC", "Mean Annual Flow", "Longitude", "Latitude",
	"Basin Area", "Mean Basin Elevation", "Range Basin Elevation", "Site Centrality"
	)

rownames(small.size.by.environment.matrix) <- c(
	"CPL", "NAP", "NPL", "SAP", "SPL", "TPL", "UMW", "WMT", "XER"
)

## Medium size
medium.size.by.environment.matrix <- dcast(
	medium.size.environment.BRT.results, ecoregion ~ var, value.var = "rel.inf"
	) %>%
	select(c(18:19, 5:6, 9, 2:3, 11, 10, 13, 12, 7, 17, 16, 4, 8, 14:15)) %>%
	as.matrix()

colnames(medium.size.by.environment.matrix) <- c(
	"Total N", "Total P", "DOC", "LWD Reach", "NAT Cover", "ALG Cover", "AQM Cover",
	"% Forested", "% Ag", "% Urban", "% ISC", "Mean Annual Flow", "Longitude", "Latitude",
	"Basin Area", "Mean Basin Elevation", "Range Basin Elevation", "Site Centrality"
	)

rownames(medium.size.by.environment.matrix) <- c(
	"CPL", "NAP", "NPL", "SAP", "SPL", "TPL", "UMW", "WMT", "XER"
)

## Large size
large.size.by.environment.matrix <- dcast(
	large.size.environment.BRT.results, ecoregion ~ var, value.var = "rel.inf"
	) %>%
	select(c(18:19, 5:6, 9, 2:3, 11, 10, 13, 12, 7, 17, 16, 4, 8, 14:15)) %>%
	as.matrix()

colnames(large.size.by.environment.matrix) <- c(
	"Total N", "Total P", "DOC", "LWD Reach", "NAT Cover", "ALG Cover", "AQM Cover",
	"% Forested", "% Ag", "% Urban", "% ISC", "Mean Annual Flow", "Longitude", "Latitude",
	"Basin Area", "Mean Basin Elevation", "Range Basin Elevation", "Site Centrality"
	)

rownames(large.size.by.environment.matrix) <- c(
	"CPL", "NAP", "NPL", "SAP", "SPL", "TPL", "UMW", "WMT", "XER"
)

## Depositional
depositional.by.environment.matrix <- dcast(
	depositional.environment.BRT.results, ecoregion ~ var, value.var = "rel.inf"
	) %>%
	select(c(18:19, 5:6, 9, 2:3, 11, 10, 13, 12, 7, 17, 16, 4, 8, 14:15)) %>%
	as.matrix()

colnames(depositional.by.environment.matrix) <- c(
	"Total N", "Total P", "DOC", "LWD Reach", "NAT Cover", "ALG Cover", "AQM Cover",
	"% Forested", "% Ag", "% Urban", "% ISC", "Mean Annual Flow", "Longitude", "Latitude",
	"Basin Area", "Mean Basin Elevation", "Range Basin Elevation", "Site Centrality"
	)

rownames(depositional.by.environment.matrix) <- c(
	"CPL", "NAP", "NPL", "SAP", "SPL", "TPL", "UMW", "WMT", "XER"
)

## Depositional-erosional
depositional.erosional.by.environment.matrix <- dcast(
	depositional.erosional.environment.BRT.results, ecoregion ~ var, value.var = "rel.inf"
	) %>%
	select(c(18:19, 5:6, 9, 2:3, 11, 10, 13, 12, 7, 17, 16, 4, 8, 14:15)) %>%
	as.matrix()

colnames(depositional.erosional.by.environment.matrix) <- c(
	"Total N", "Total P", "DOC", "LWD Reach", "NAT Cover", "ALG Cover", "AQM Cover",
	"% Forested", "% Ag", "% Urban", "% ISC", "Mean Annual Flow", "Longitude", "Latitude",
	"Basin Area", "Mean Basin Elevation", "Range Basin Elevation", "Site Centrality"
	)

rownames(depositional.erosional.by.environment.matrix) <- c(
	"CPL", "NAP", "NPL", "SAP", "SPL", "TPL", "UMW", "WMT", "XER"
)

## Erosional
erosional.by.environment.matrix <- dcast(
	erosional.environment.BRT.results, ecoregion ~ var, value.var = "rel.inf"
	) %>%
	select(c(18:19, 5:6, 9, 2:3, 11, 10, 13, 12, 7, 17, 16, 4, 8, 14:15)) %>%
	as.matrix()

colnames(erosional.by.environment.matrix) <- c(
	"Total N", "Total P", "DOC", "LWD Reach", "NAT Cover", "ALG Cover", "AQM Cover",
	"% Forested", "% Ag", "% Urban", "% ISC", "Mean Annual Flow", "Longitude", "Latitude",
	"Basin Area", "Mean Basin Elevation", "Range Basin Elevation", "Site Centrality"
	)

rownames(erosional.by.environment.matrix) <- c(
	"CPL", "NAP", "NPL", "SAP", "SPL", "TPL", "UMW", "WMT", "XER"
)

## Cold water
cold.water.by.environment.matrix <- dcast(
	cold.water.environment.BRT.results, ecoregion ~ var, value.var = "rel.inf"
	) %>%
	select(c(18:19, 5:6, 9, 2:3, 11, 10, 13, 12, 7, 17, 16, 4, 8, 14:15)) %>%
	as.matrix()

colnames(cold.water.by.environment.matrix) <- c(
	"Total N", "Total P", "DOC", "LWD Reach", "NAT Cover", "ALG Cover", "AQM Cover",
	"% Forested", "% Ag", "% Urban", "% ISC", "Mean Annual Flow", "Longitude", "Latitude",
	"Basin Area", "Mean Basin Elevation", "Range Basin Elevation", "Site Centrality"
	)

rownames(cold.water.by.environment.matrix) <- c(
	"CPL", "NAP", "NPL", "SAP", "SPL", "TPL", "UMW", "WMT", "XER"
)

## Cool-warm water
cool.warm.water.by.environment.matrix <- dcast(
	cool.warm.water.environment.BRT.results, ecoregion ~ var, value.var = "rel.inf"
	) %>%
	select(c(18:19, 5:6, 9, 2:3, 11, 10, 13, 12, 7, 17, 16, 4, 8, 14:15)) %>%
	as.matrix()

colnames(cool.warm.water.by.environment.matrix) <- c(
	"Total N", "Total P", "DOC", "LWD Reach", "NAT Cover", "ALG Cover", "AQM Cover",
	"% Forested", "% Ag", "% Urban", "% ISC", "Mean Annual Flow", "Longitude", "Latitude",
	"Basin Area", "Mean Basin Elevation", "Range Basin Elevation", "Site Centrality"
	)

rownames(cool.warm.water.by.environment.matrix) <- c(
	"CPL", "NAP", "NPL", "SAP", "SPL", "TPL", "UMW", "WMT", "XER"
)

## Warm water
warm.water.by.environment.matrix <- dcast(
	warm.water.environment.BRT.results, ecoregion ~ var, value.var = "rel.inf"
	) %>%
	select(c(18:19, 5:6, 9, 2:3, 11, 10, 13, 12, 7, 17, 16, 4, 8, 14:15)) %>%
	as.matrix()

colnames(warm.water.by.environment.matrix) <- c(
	"Total N", "Total P", "DOC", "LWD Reach", "NAT Cover", "ALG Cover", "AQM Cover",
	"% Forested", "% Ag", "% Urban", "% ISC", "Mean Annual Flow", "Longitude", "Latitude",
	"Basin Area", "Mean Basin Elevation", "Range Basin Elevation", "Site Centrality"
	)

rownames(warm.water.by.environment.matrix) <- c(
	"CPL", "NAP", "NPL", "SAP", "SPL", "TPL", "UMW", "WMT", "XER"
)

## CG
CG.by.environment.matrix <- dcast(
	CG.environment.BRT.results, ecoregion ~ var, value.var = "rel.inf"
	) %>%
	select(c(18:19, 5:6, 9, 2:3, 11, 10, 13, 12, 7, 17, 16, 4, 8, 14:15)) %>%
	as.matrix()

colnames(CG.by.environment.matrix) <- c(
	"Total N", "Total P", "DOC", "LWD Reach", "NAT Cover", "ALG Cover", "AQM Cover",
	"% Forested", "% Ag", "% Urban", "% ISC", "Mean Annual Flow", "Longitude", "Latitude",
	"Basin Area", "Mean Basin Elevation", "Range Basin Elevation", "Site Centrality"
	)

rownames(CG.by.environment.matrix) <- c(
	"CPL", "NAP", "NPL", "SAP", "SPL", "TPL", "UMW", "WMT", "XER"
)

## CF
CF.by.environment.matrix <- dcast(
	CF.environment.BRT.results, ecoregion ~ var, value.var = "rel.inf"
	) %>%
	select(c(18:19, 5:6, 9, 2:3, 11, 10, 13, 12, 7, 17, 16, 4, 8, 14:15)) %>%
	as.matrix()

colnames(CF.by.environment.matrix) <- c(
	"Total N", "Total P", "DOC", "LWD Reach", "NAT Cover", "ALG Cover", "AQM Cover",
	"% Forested", "% Ag", "% Urban", "% ISC", "Mean Annual Flow", "Longitude", "Latitude",
	"Basin Area", "Mean Basin Elevation", "Range Basin Elevation", "Site Centrality"
	)

rownames(CF.by.environment.matrix) <- c(
	"CPL", "NAP", "NPL", "SAP", "SPL", "TPL", "UMW", "WMT", "XER"
)

## HB
HB.by.environment.matrix <- dcast(
	HB.environment.BRT.results, ecoregion ~ var, value.var = "rel.inf"
	) %>%
	select(c(18:19, 5:6, 9, 2:3, 11, 10, 13, 12, 7, 17, 16, 4, 8, 14:15)) %>%
	as.matrix()

colnames(HB.by.environment.matrix) <- c(
	"Total N", "Total P", "DOC", "LWD Reach", "NAT Cover", "ALG Cover", "AQM Cover",
	"% Forested", "% Ag", "% Urban", "% ISC", "Mean Annual Flow", "Longitude", "Latitude",
	"Basin Area", "Mean Basin Elevation", "Range Basin Elevation", "Site Centrality"
	)

rownames(HB.by.environment.matrix) <- c(
	"CPL", "NAP", "NPL", "SAP", "SPL", "TPL", "UMW", "WMT", "XER"
)

## PR
PR.by.environment.matrix <- dcast(
	PR.environment.BRT.results, ecoregion ~ var, value.var = "rel.inf"
	) %>%
	select(c(18:19, 5:6, 9, 2:3, 11, 10, 13, 12, 7, 17, 16, 4, 8, 14:15)) %>%
	as.matrix()

colnames(PR.by.environment.matrix) <- c(
	"Total N", "Total P", "DOC", "LWD Reach", "NAT Cover", "ALG Cover", "AQM Cover",
	"% Forested", "% Ag", "% Urban", "% ISC", "Mean Annual Flow", "Longitude", "Latitude",
	"Basin Area", "Mean Basin Elevation", "Range Basin Elevation", "Site Centrality"
	)

rownames(PR.by.environment.matrix) <- c(
	"CPL", "NAP", "NPL", "SAP", "SPL", "TPL", "UMW", "WMT", "XER"
)

## Sensitive tolerance
sensitive.tolerance.by.environment.matrix <- dcast(
	sensitive.tolerance.environment.BRT.results, ecoregion ~ var, value.var = "rel.inf"
	) %>%
	select(c(18:19, 5:6, 9, 2:3, 11, 10, 13, 12, 7, 17, 16, 4, 8, 14:15)) %>%
	as.matrix()

colnames(sensitive.tolerance.by.environment.matrix) <- c(
	"Total N", "Total P", "DOC", "LWD Reach", "NAT Cover", "ALG Cover", "AQM Cover",
	"% Forested", "% Ag", "% Urban", "% ISC", "Mean Annual Flow", "Longitude", "Latitude",
	"Basin Area", "Mean Basin Elevation", "Range Basin Elevation", "Site Centrality"
	)

rownames(sensitive.tolerance.by.environment.matrix) <- c(
	"CPL", "NAP", "NPL", "SAP", "SPL", "TPL", "UMW", "WMT", "XER"
)

## Medium tolerance
intermediate.tolerance.by.environment.matrix <- dcast(
	intermediate.tolerance.environment.BRT.results, ecoregion ~ var, value.var = "rel.inf"
	) %>%
	select(c(18:19, 5:6, 9, 2:3, 11, 10, 13, 12, 7, 17, 16, 4, 8, 14:15)) %>%
	as.matrix()

colnames(intermediate.tolerance.by.environment.matrix) <- c(
	"Total N", "Total P", "DOC", "LWD Reach", "NAT Cover", "ALG Cover", "AQM Cover",
	"% Forested", "% Ag", "% Urban", "% ISC", "Mean Annual Flow", "Longitude", "Latitude",
	"Basin Area", "Mean Basin Elevation", "Range Basin Elevation", "Site Centrality"
	)

rownames(intermediate.tolerance.by.environment.matrix) <- c(
	"CPL", "NAP", "NPL", "SAP", "SPL", "TPL", "UMW", "WMT", "XER"
)

## Tolerant
tolerant.by.environment.matrix <- dcast(
	tolerant.environment.BRT.results, ecoregion ~ var, value.var = "rel.inf"
	) %>%
	select(c(18:19, 5:6, 9, 2:3, 11, 10, 13, 12, 7, 17, 16, 4, 8, 14:15)) %>%
	as.matrix()

colnames(tolerant.by.environment.matrix) <- c(
	"Total N", "Total P", "DOC", "LWD Reach", "NAT Cover", "ALG Cover", "AQM Cover",
	"% Forested", "% Ag", "% Urban", "% ISC", "Mean Annual Flow", "Longitude", "Latitude",
	"Basin Area", "Mean Basin Elevation", "Range Basin Elevation", "Site Centrality"
	)

rownames(tolerant.by.environment.matrix) <- c(
	"CPL", "NAP", "NPL", "SAP", "SPL", "TPL", "UMW", "WMT", "XER"
)
```





```{r Low Dispersal Relative Influence, echo = FALSE}
kable(
	low.dispersal.by.environment.matrix,
	booktabs = TRUE,
	digits = 2,
	caption = "Table of relative influence values for predictors in the low dispersal-by-environment boosted regression trees, with relative influence values provided for each ecoregion."
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped", "scale_down")) %>%
	landscape()
```

```{r High Dispersal Relative Influence, echo = FALSE}
kable(
	high.dispersal.by.environment.matrix,
	booktabs = TRUE,
	digits = 2,
	caption = "Table of relative influence values for predictors in the high dispersal-by-environment boosted regression trees, with relative influence values provided for each ecoregion."
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped", "scale_down")) %>%
	landscape()
```

```{r Nonflyer Relative Influence, echo = FALSE}
kable(
	nonflyer.by.environment.matrix,
	booktabs = TRUE,
	digits = 2,
	caption = "Table of relative influence values for predictors in the nonflyer-by-environment boosted regression trees, with relative influence values provided for each ecoregion."
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped", "scale_down")) %>%
	landscape()
```

```{r Weak Flyer Relative Influence, echo = FALSE}
kable(
	weak.flyer.by.environment.matrix,
	booktabs = TRUE,
	digits = 2,
	caption = "Table of relative influence values for predictors in the weak flyer-by-environment boosted regression trees, with relative influence values provided for each ecoregion."
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped", "scale_down")) %>%
	landscape()
```

```{r Strong Flyer Relative Influence, echo = FALSE}
kable(
	strong.flyer.by.environment.matrix,
	booktabs = TRUE,
	digits = 2,
	caption = "Table of relative influence values for predictors in the strong flyer-by-environment boosted regression trees, with relative influence values provided for each ecoregion."
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped", "scale_down")) %>%
	landscape()
```

```{r Small Size Relative Influence, echo = FALSE}
kable(
	small.size.by.environment.matrix,
	booktabs = TRUE,
	digits = 2,
	caption = "Table of relative influence values for predictors in the small size-by-environment boosted regression trees, with relative influence values provided for each ecoregion."
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped", "scale_down")) %>%
	landscape()
```

```{r Medium Size Relative Influence, echo = FALSE}
kable(
	medium.size.by.environment.matrix,
	booktabs = TRUE,
	digits = 2,
	caption = "Table of relative influence values for predictors in the medium size-by-environment boosted regression trees, with relative influence values provided for each ecoregion."
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped", "scale_down")) %>%
	landscape()
```

```{r Large Size Relative Influence, echo = FALSE}
kable(
	large.size.by.environment.matrix,
	booktabs = TRUE,
	digits = 2,
	caption = "Table of relative influence values for predictors in the large size-by-environment boosted regression trees, with relative influence values provided for each ecoregion."
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped", "scale_down")) %>%
	landscape()
```

```{r Depositional Relative Influence, echo = FALSE}
kable(
	depositional.by.environment.matrix,
	booktabs = TRUE,
	digits = 2,
	caption = "Table of relative influence values for predictors in the depositional-by-environment boosted regression trees, with relative influence values provided for each ecoregion."
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped", "scale_down")) %>%
	landscape()
```

```{r Depositional-Erosional Relative Influence, echo = FALSE}
kable(
	depositional.erosional.by.environment.matrix,
	booktabs = TRUE,
	digits = 2,
	caption = "Table of relative influence values for predictors in the depositional-erosional-by-environment boosted regression trees, with relative influence values provided for each ecoregion."
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped", "scale_down")) %>%
	landscape()
```

```{r Erosional Relative Influence, echo = FALSE}
kable(
	erosional.by.environment.matrix,
	booktabs = TRUE,
	digits = 2,
	caption = "Table of relative influence values for predictors in the erosional-by-environment boosted regression trees, with relative influence values provided for each ecoregion."
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped", "scale_down")) %>%
	landscape()
```

```{r Cold Water Relative Influence, echo = FALSE}
kable(
	cold.water.by.environment.matrix,
	booktabs = TRUE,
	digits = 2,
	caption = "Table of relative influence values for predictors in the cold water-by-environment boosted regression trees, with relative influence values provided for each ecoregion."
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped", "scale_down")) %>%
	landscape()
```

```{r Cool-Warm Water Relative Influence, echo = FALSE}
kable(
	cool.warm.water.by.environment.matrix,
	booktabs = TRUE,
	digits = 2,
	caption = "Table of relative influence values for predictors in the cool-warm water-by-environment boosted regression trees, with relative influence values provided for each ecoregion."
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped", "scale_down")) %>%
	landscape()
```

```{r Warm Water Relative Influence, echo = FALSE}
kable(
	warm.water.by.environment.matrix,
	booktabs = TRUE,
	digits = 2,
	caption = "Table of relative influence values for predictors in the warm water-by-environment boosted regression trees, with relative influence values provided for each ecoregion."
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped", "scale_down")) %>%
	landscape()
```

```{r Sensitive Tolerance Relative Influence, echo = FALSE}
kable(
	sensitive.tolerance.by.environment.matrix,
	booktabs = TRUE,
	digits = 2,
	caption = "Table of relative influence values for predictors in the sensitive tolerance-by-environment boosted regression trees, with relative influence values provided for each ecoregion."
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped", "scale_down")) %>%
	landscape()
```

```{r Intermediate Tolerance Relative Influence, echo = FALSE}
kable(
	sensitive.tolerance.by.environment.matrix,
	booktabs = TRUE,
	digits = 2,
	caption = "Table of relative influence values for predictors in the intermediate tolerance-by-environment boosted regression trees, with relative influence values provided for each ecoregion."
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped", "scale_down")) %>%
	landscape()
```

```{r Tolerant Relative Influence, echo = FALSE}
kable(
	tolerant.by.environment.matrix,
	booktabs = TRUE,
	digits = 2,
	caption = "Table of relative influence values for predictors in the tolerant-by-environment boosted regression trees, with relative influence values provided for each ecoregion."
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped", "scale_down")) %>%
	landscape()
```

```{r CG Relative Influence, echo = FALSE}
kable(
	CG.by.environment.matrix,
	booktabs = TRUE,
	digits = 2,
	caption = "Table of relative influence values for predictors in the collector-gatherer-by-environment boosted regression trees, with relative influence values provided for each ecoregion."
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped", "scale_down")) %>%
	landscape()
```

```{r CF Relative Influence, echo = FALSE}
kable(
	CF.by.environment.matrix,
	booktabs = TRUE,
	digits = 2,
	caption = "Table of relative influence values for predictors in the collector-filterer-by-environment boosted regression trees, with relative influence values provided for each ecoregion."
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped", "scale_down")) %>%
	landscape()
```

```{r HB Relative Influence, echo = FALSE}
kable(
	HB.by.environment.matrix,
	booktabs = TRUE,
	digits = 2,
	caption = "Table of relative influence values for predictors in the herbivore-by-environment boosted regression trees, with relative influence values provided for each ecoregion."
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped", "scale_down")) %>%
	landscape()
```

```{r PR Relative Influence, echo = FALSE}
kable(
	PR.by.environment.matrix,
	booktabs = TRUE,
	digits = 2,
	caption = "Table of relative influence values for predictors in the predator-by-environment boosted regression trees, with relative influence values provided for each ecoregion."
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped", "scale_down")) %>%
	landscape()
```





```{r Filtered Traits-by-Environment Results, include = FALSE}
## Filter data to only include variables with a relative influence >= 5.00

## Low dispersal
low.dispersal.threshold.RI <- low.dispersal.environment.BRT.results %>%
	filter(rel.inf > 5.00) %>%
	group_by(ecoregion, predictor.type) %>%
	summarise(summed.RI = sum(rel.inf))

## High dispersal
high.dispersal.threshold.RI <- high.dispersal.environment.BRT.results %>%
	filter(rel.inf > 5.00) %>%
	group_by(ecoregion, predictor.type) %>%
	summarise(summed.RI = sum(rel.inf))

## Nonflyer
nonflyer.threshold.RI <- nonflyer.environment.BRT.results %>%
	filter(rel.inf > 5.00) %>%
	group_by(ecoregion, predictor.type) %>%
	summarise(summed.RI = sum(rel.inf))

## Weak flyer
weak.flyer.threshold.RI <- weak.flyer.environment.BRT.results %>%
	filter(rel.inf > 5.00) %>%
	group_by(ecoregion, predictor.type) %>%
	summarise(summed.RI = sum(rel.inf))

## Strong flyer
strong.flyer.threshold.RI <- strong.flyer.environment.BRT.results %>%
	filter(rel.inf > 5.00) %>%
	group_by(ecoregion, predictor.type) %>%
	summarise(summed.RI = sum(rel.inf))

## Small size
small.size.threshold.RI <- small.size.environment.BRT.results %>%
	filter(rel.inf > 5.00) %>%
	group_by(ecoregion, predictor.type) %>%
	summarise(summed.RI = sum(rel.inf))

## Medium size
medium.size.threshold.RI <- medium.size.environment.BRT.results %>%
	filter(rel.inf > 5.00) %>%
	group_by(ecoregion, predictor.type) %>%
	summarise(summed.RI = sum(rel.inf))

## Large size
large.size.threshold.RI <- large.size.environment.BRT.results %>%
	filter(rel.inf > 5.00) %>%
	group_by(ecoregion, predictor.type) %>%
	summarise(summed.RI = sum(rel.inf))

## Depositional
depositional.threshold.RI <- depositional.environment.BRT.results %>%
	filter(rel.inf > 5.00) %>%
	group_by(ecoregion, predictor.type) %>%
	summarise(summed.RI = sum(rel.inf))

## Depositional-erosional
depositional.erosional.threshold.RI <- depositional.erosional.environment.BRT.results %>%
	filter(rel.inf > 5.00) %>%
	group_by(ecoregion, predictor.type) %>%
	summarise(summed.RI = sum(rel.inf))

## Erosional
erosional.threshold.RI <- erosional.environment.BRT.results %>%
	filter(rel.inf > 5.00) %>%
	group_by(ecoregion, predictor.type) %>%
	summarise(summed.RI = sum(rel.inf))

## Cold water
cold.water.threshold.RI <- cold.water.environment.BRT.results %>%
	filter(rel.inf > 5.00) %>%
	group_by(ecoregion, predictor.type) %>%
	summarise(summed.RI = sum(rel.inf))

## Cool-warm water
cool.warm.water.threshold.RI <- cool.warm.water.environment.BRT.results %>%
	filter(rel.inf > 5.00) %>%
	group_by(ecoregion, predictor.type) %>%
	summarise(summed.RI = sum(rel.inf))

## Warm water
warm.water.threshold.RI <- warm.water.environment.BRT.results %>%
	filter(rel.inf > 5.00) %>%
	group_by(ecoregion, predictor.type) %>%
	summarise(summed.RI = sum(rel.inf))

## Sensitive tolerance
sensitive.tolerance.threshold.RI <- sensitive.tolerance.environment.BRT.results %>%
	filter(rel.inf > 5.00) %>%
	group_by(ecoregion, predictor.type) %>%
	summarise(summed.RI = sum(rel.inf))

## Intermediate tolerance
intermediate.tolerance.threshold.RI <- intermediate.tolerance.environment.BRT.results %>%
	filter(rel.inf > 5.00) %>%
	group_by(ecoregion, predictor.type) %>%
	summarise(summed.RI = sum(rel.inf))

## Tolerant
tolerant.threshold.RI <- tolerant.environment.BRT.results %>%
	filter(rel.inf > 5.00) %>%
	group_by(ecoregion, predictor.type) %>%
	summarise(summed.RI = sum(rel.inf))

## CG
CG.threshold.RI <- CG.environment.BRT.results %>%
	filter(rel.inf > 5.00) %>%
	group_by(ecoregion, predictor.type) %>%
	summarise(summed.RI = sum(rel.inf))

## CF
CF.threshold.RI <- CF.environment.BRT.results %>%
	filter(rel.inf > 5.00) %>%
	group_by(ecoregion, predictor.type) %>%
	summarise(summed.RI = sum(rel.inf))

## HB
HB.threshold.RI <- HB.environment.BRT.results %>%
	filter(rel.inf > 5.00) %>%
	group_by(ecoregion, predictor.type) %>%
	summarise(summed.RI = sum(rel.inf))

## PR
PR.threshold.RI <- PR.environment.BRT.results %>%
	filter(rel.inf > 5.00) %>%
	group_by(ecoregion, predictor.type) %>%
	summarise(summed.RI = sum(rel.inf))
```





```{r Low Dispersal-by-Environment Summed Relative Influence, echo = FALSE}
kable(
	low.dispersal.threshold.RI,
	booktabs = TRUE,
	digits = 2,
	caption = "Summed relative influence for all predictor variables within the respective category with a relative influence >5.00 for the low dispersal-by-environment boosted regression trees. Summed relative influence was calculated for each of the ecoregions.",
	col.names = c("Ecoregion", "Predictor Category", "Relative Influence")
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped"))
```

```{r High Dispersal-by-Environment Summed Relative Influence, echo = FALSE}
kable(
	high.dispersal.threshold.RI,
	booktabs = TRUE,
	digits = 2,
	caption = "Summed relative influence for all predictor variables within the respective category with a relative influence >5.00 for the high dispersal-by-environment boosted regression trees. Summed relative influence was calculated for each of the ecoregions.",
	col.names = c("Ecoregion", "Predictor Category", "Relative Influence")
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped"))
```

```{r Nonflyer-by-Environment Summed Relative Influence, echo = FALSE}
kable(
	nonflyer.threshold.RI,
	booktabs = TRUE,
	digits = 2,
	caption = "Summed relative influence for all predictor variables within the respective category with a relative influence >5.00 for the nonflyer-by-environment boosted regression trees. Summed relative influence was calculated for each of the ecoregions.",
	col.names = c("Ecoregion", "Predictor Category", "Relative Influence")
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped"))
```

```{r Weak Flyer-by-Environment Summed Relative Influence, echo = FALSE}
kable(
	weak.flyer.threshold.RI,
	booktabs = TRUE,
	digits = 2,
	caption = "Summed relative influence for all predictor variables within the respective category with a relative influence >5.00 for the weak flyer-by-environment boosted regression trees. Summed relative influence was calculated for each of the ecoregions.",
	col.names = c("Ecoregion", "Predictor Category", "Relative Influence")
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped"))
```

```{r Strong Flyer-by-Environment Summed Relative Influence, echo = FALSE}
kable(
	strong.flyer.threshold.RI,
	booktabs = TRUE,
	digits = 2,
	caption = "Summed relative influence for all predictor variables within the respective category with a relative influence >5.00 for the strong flyer-by-environment boosted regression trees. Summed relative influence was calculated for each of the ecoregions.",
	col.names = c("Ecoregion", "Predictor Category", "Relative Influence")
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped"))
```

```{r Small Size-by-Environment Summed Relative Influence, echo = FALSE}
kable(
	small.size.threshold.RI,
	booktabs = TRUE,
	digits = 2,
	caption = "Summed relative influence for all predictor variables within the respective category with a relative influence >5.00 for the small size-by-environment boosted regression trees. Summed relative influence was calculated for each of the ecoregions.",
	col.names = c("Ecoregion", "Predictor Category", "Relative Influence")
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped"))
```

```{r Medium Size-by-Environment Summed Relative Influence, echo = FALSE}
kable(
	medium.size.threshold.RI,
	booktabs = TRUE,
	digits = 2,
	caption = "Summed relative influence for all predictor variables within the respective category with a relative influence >5.00 for the medium size-by-environment boosted regression trees. Summed relative influence was calculated for each of the ecoregions.",
	col.names = c("Ecoregion", "Predictor Category", "Relative Influence")
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped"))
```

```{r Large Size-by-Environment Summed Relative Influence, echo = FALSE}
kable(
	large.size.threshold.RI,
	booktabs = TRUE,
	digits = 2,
	caption = "Summed relative influence for all predictor variables within the respective category with a relative influence >5.00 for the large size-by-environment boosted regression trees. Summed relative influence was calculated for each of the ecoregions.",
	col.names = c("Ecoregion", "Predictor Category", "Relative Influence")
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped"))
```

```{r Depositional-by-Environment Summed Relative Influence, echo = FALSE}
kable(
	depositional.threshold.RI,
	booktabs = TRUE,
	digits = 2,
	caption = "Summed relative influence for all predictor variables within the respective category with a relative influence >5.00 for the depositional-by-environment boosted regression trees. Summed relative influence was calculated for each of the ecoregions.",
	col.names = c("Ecoregion", "Predictor Category", "Relative Influence")
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped"))
```

```{r Depositional-Erosional-by-Environment Summed Relative Influence, echo = FALSE}
kable(
	depositional.erosional.threshold.RI,
	booktabs = TRUE,
	digits = 2,
	caption = "Summed relative influence for all predictor variables within the respective category with a relative influence >5.00 for the depositional-erosional-by-environment boosted regression trees. Summed relative influence was calculated for each of the ecoregions.",
	col.names = c("Ecoregion", "Predictor Category", "Relative Influence")
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped"))
```

```{r Erosional-by-Environment Summed Relative Influence, echo = FALSE}
kable(
	erosional.threshold.RI,
	booktabs = TRUE,
	digits = 2,
	caption = "Summed relative influence for all predictor variables within the respective category with a relative influence >5.00 for the erosional-by-environment boosted regression trees. Summed relative influence was calculated for each of the ecoregions.",
	col.names = c("Ecoregion", "Predictor Category", "Relative Influence")
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped"))
```

```{r Cold Water-by-Environment Summed Relative Influence, echo = FALSE}
kable(
	cold.water.threshold.RI,
	booktabs = TRUE,
	digits = 2,
	caption = "Summed relative influence for all predictor variables within the respective category with a relative influence >5.00 for the cold water-by-environment boosted regression trees. Summed relative influence was calculated for each of the ecoregions.",
	col.names = c("Ecoregion", "Predictor Category", "Relative Influence")
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped"))
```

```{r Cool-Warm Water-by-Environment Summed Relative Influence, echo = FALSE}
kable(
	cool.warm.water.threshold.RI,
	booktabs = TRUE,
	digits = 2,
	caption = "Summed relative influence for all predictor variables within the respective category with a relative influence >5.00 for the cool-warm water-by-environment boosted regression trees. Summed relative influence was calculated for each of the ecoregions.",
	col.names = c("Ecoregion", "Predictor Category", "Relative Influence")
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped"))
```

```{r Warm Water-by-Environment Summed Relative Influence, echo = FALSE}
kable(
	warm.water.threshold.RI,
	booktabs = TRUE,
	digits = 2,
	caption = "Summed relative influence for all predictor variables within the respective category with a relative influence >5.00 for the warm water-by-environment boosted regression trees. Summed relative influence was calculated for each of the ecoregions.",
	col.names = c("Ecoregion", "Predictor Category", "Relative Influence")
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped"))
```

```{r Sensitive Tolerance-by-Environment Summed Relative Influence, echo = FALSE}
kable(
	sensitive.tolerance.threshold.RI,
	booktabs = TRUE,
	digits = 2,
	caption = "Summed relative influence for all predictor variables within the respective category with a relative influence >5.00 for the sensitive tolerance-by-environment boosted regression trees. Summed relative influence was calculated for each of the ecoregions.",
	col.names = c("Ecoregion", "Predictor Category", "Relative Influence")
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped"))
```

```{r Intermediate Tolerance-by-Environment Summed Relative Influence, echo = FALSE}
kable(
	intermediate.tolerance.threshold.RI,
	booktabs = TRUE,
	digits = 2,
	caption = "Summed relative influence for all predictor variables within the respective category with a relative influence >5.00 for the intermediate tolerance-by-environment boosted regression trees. Summed relative influence was calculated for each of the ecoregions.",
	col.names = c("Ecoregion", "Predictor Category", "Relative Influence")
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped"))
```

```{r Tolerant-by-Environment Summed Relative Influence, echo = FALSE}
kable(
	tolerant.threshold.RI,
	booktabs = TRUE,
	digits = 2,
	caption = "Summed relative influence for all predictor variables within the respective category with a relative influence >5.00 for the tolerant-by-environment boosted regression trees. Summed relative influence was calculated for each of the ecoregions.",
	col.names = c("Ecoregion", "Predictor Category", "Relative Influence")
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped"))
```

```{r CG-by-Environment Summed Relative Influence, echo = FALSE}
kable(
	CG.threshold.RI,
	booktabs = TRUE,
	digits = 2,
	caption = "Summed relative influence for all predictor variables within the respective category with a relative influence >5.00 for the collector-gatherer-by-environment boosted regression trees. Summed relative influence was calculated for each of the ecoregions.",
	col.names = c("Ecoregion", "Predictor Category", "Relative Influence")
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped"))
```

```{r CF-by-Environment Summed Relative Influence, echo = FALSE}
kable(
	CF.threshold.RI,
	booktabs = TRUE,
	digits = 2,
	caption = "Summed relative influence for all predictor variables within the respective category with a relative influence >5.00 for the collector-filterer-by-environment boosted regression trees. Summed relative influence was calculated for each of the ecoregions.",
	col.names = c("Ecoregion", "Predictor Category", "Relative Influence")
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped"))
```

```{r HB-by-Environment Summed Relative Influence, echo = FALSE}
kable(
	HB.threshold.RI,
	booktabs = TRUE,
	digits = 2,
	caption = "Summed relative influence for all predictor variables within the respective category with a relative influence >5.00 for the herbivore-by-environment boosted regression trees. Summed relative influence was calculated for each of the ecoregions.",
	col.names = c("Ecoregion", "Predictor Category", "Relative Influence")
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped"))
```

```{r PR-by-Environment Summed Relative Influence, echo = FALSE}
kable(
	PR.threshold.RI,
	booktabs = TRUE,
	digits = 2,
	caption = "Summed relative influence for all predictor variables within the respective category with a relative influence >5.00 for the predator-by-environment boosted regression trees. Summed relative influence was calculated for each of the ecoregions.",
	col.names = c("Ecoregion", "Predictor Category", "Relative Influence")
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped"))
```





\newpage
# R Session Information

```{r R Packages, echo = FALSE}
df_session_packages <- devtools::session_info()$packages %>% 
  as.data.frame(.) %>% 
  filter(attached == TRUE) %>% 
  dplyr::select(loadedversion, date) %>% 
  rownames_to_column

colnames(df_session_packages) <- c("Package", "Loaded Version", "Date")

kable(
  df_session_packages, 
  booktabs = TRUE,
  caption = "Packages required for data management and summaries."
  ) %>%
	kable_styling(
		full_width = FALSE,
  	latex_options = c("HOLD_position", "striped")
  	) 
```




