---
title: "Environmental filtering and habitat (mis)matching of riverine invertebrate communities"
subtitle: "NRSA DisEQ-Predictor Variable Summary Tables"
output:
  pdf_document:
    fig_caption: yes
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
knitr::opts_chunk$set(results = "hold", fig.pos = "H", fig.align = "center", out.width = "92.5%")
options(knitr.graphics.error = FALSE)
kableExtra::usepackage_latex("float")
```

```{r Load Package for R Markdown, include = FALSE}
library(kableExtra)
library(knitr)
```

```{r Load Packages & Data, include = FALSE}
library(tidyverse)

## Load the reduced workspace
load("data_analysis/2-DisEQ_analyses/2-DisEQ_analyses-Reduced_Workspace.RData")
```


\newpage
# Environmental Variable Summaries

Supplemental tables with summaries (i.e., mean and standard deviation) for each variable within the environmental category.

List of environmental variables:

+ total N
+ total P
+ Dissolved organic carbon (DOC)
+ Large Woody Debris in reach (LWD)
+ Natural (NAT) cover
+ Algal (ALG) cover
+ Aquatic macrophyte (AQM) cover


```{r Numerical Summaries: Environmental Variables, include = FALSE}
## Total N
total.N.summary <- final.DisEQ.data %>%
	select(ecoregion, total.N) %>%
	group_by(ecoregion) %>%
	summarise(Mean = mean(total.N), SD = sd(total.N))

## Total P
total.P.summary <- final.DisEQ.data %>%
	select(ecoregion, total.P) %>%
	group_by(ecoregion) %>%
	summarise(Mean = mean(total.P), SD = sd(total.P))

## DOC
DOC.summary <- final.DisEQ.data %>%
	select(ecoregion, DOC) %>%
	group_by(ecoregion) %>%
	summarise(Mean = mean(DOC), SD = sd(DOC))

## LWD Reach
LWD.reach.summary <- final.DisEQ.data %>%
	select(ecoregion, LWD.reach) %>%
	group_by(ecoregion) %>%
	summarise(Mean = mean(LWD.reach), SD = sd(LWD.reach))

## NAT Cover
NAT.cover.summary <- final.DisEQ.data %>%
	select(ecoregion, NAT.cover) %>%
	group_by(ecoregion) %>%
	summarise(Mean = mean(NAT.cover), SD = sd(NAT.cover))

## ALG Cover
ALG.cover.summary <- final.DisEQ.data %>%
	select(ecoregion, ALG.cover) %>%
	group_by(ecoregion) %>%
	summarise(Mean = mean(ALG.cover), SD = sd(ALG.cover))

## AQM Cover
AQM.cover.summary <- final.DisEQ.data %>%
	select(ecoregion, AQM.cover) %>%
	group_by(ecoregion) %>%
	summarise(Mean = mean(AQM.cover), SD = sd(AQM.cover))
```


```{r Total N Summary, echo = FALSE}
kable(
	total.N.summary,
	booktabs = TRUE,
	digits = 2,
	col.names = c("Ecoregion", "Mean", "SD"),
	caption = "Summary of total N by ecoregion."
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r Total P Summary, echo = FALSE}
kable(
	total.P.summary,
	booktabs = TRUE,
	digits = 2,
	col.names = c("Ecoregion", "Mean", "SD"),
	caption = "Summary of total P by ecoregion."
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r DOC Summary, echo = FALSE}
kable(
	DOC.summary,
	booktabs = TRUE,
	digits = 2,
	col.names = c("Ecoregion", "Mean", "SD"),
	caption = "Summary of DOC by ecoregion."
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r LWD Summary, echo = FALSE}
kable(
	LWD.reach.summary,
	booktabs = TRUE,
	digits = 2,
	col.names = c("Ecoregion", "Mean", "SD"),
	caption = "Summary of LWD by ecoregion."
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r NAT Cover Summary, echo = FALSE}
kable(
	NAT.cover.summary,
	booktabs = TRUE,
	digits = 2,
	col.names = c("Ecoregion", "Mean", "SD"),
	caption = "Summary of NAT cover by ecoregion."
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r ALG Cover Summary, echo = FALSE}
kable(
	ALG.cover.summary,
	booktabs = TRUE,
	digits = 2,
	col.names = c("Ecoregion", "Mean", "SD"),
	caption = "Summary of ALG cover by ecoregion."
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r AQM Cover Summary, echo = FALSE}
kable(
	AQM.cover.summary,
	booktabs = TRUE,
	digits = 2,
	col.names = c("Ecoregion", "Mean", "SD"),
	caption = "Summary of AQM cover by ecoregion."
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped"))
```



\newpage
# Landscape Variable Summaries

Supplemental tables with summaries (i.e., mean and standard deviation) for each variable within the landscape category.

List of landscape variables:

+ % forested land cover
+ % agricultural land cover
+ % urban land cover
+ % impervious surface land cover


```{r Numerical Summaries: Landscape Variables, include = FALSE}
## % Forested
pct.for.summary <- final.DisEQ.data %>%
	select(ecoregion, pct.for) %>%
	group_by(ecoregion) %>%
	summarise(Mean = mean(pct.for), SD = sd(pct.for))

## % Agricultural
pct.ag.summary <- final.DisEQ.data %>%
	select(ecoregion, pct.ag) %>%
	group_by(ecoregion) %>%
	summarise(Mean = mean(pct.ag), SD = sd(pct.ag))

## % Urban
pct.urb.summary <- final.DisEQ.data %>%
	select(ecoregion, pct.urb) %>%
	group_by(ecoregion) %>%
	summarise(Mean = mean(pct.urb), SD = sd(pct.urb))

## % Impervious Surface Cover
pct.ISC.summary <- final.DisEQ.data %>%
	select(ecoregion, pct.ISC) %>%
	group_by(ecoregion) %>%
	summarise(Mean = mean(pct.ISC), SD = sd(pct.ISC))
```


```{r Forested Land Cover Summary, echo = FALSE}
kable(
	pct.for.summary,
	booktabs = TRUE,
	digits = 2,
	col.names = c("Ecoregion", "Mean", "SD"),
	caption = "Summary of \\% forested land cover by ecoregion."
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r Agricultural Land Cover Summary, echo = FALSE}
kable(
	pct.ag.summary,
	booktabs = TRUE,
	digits = 2,
	col.names = c("Ecoregion", "Mean", "SD"),
	caption = "Summary of \\% agricultural land cover by ecoregion."
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r Urban Land Cover Summary, echo = FALSE}
kable(
	pct.urb.summary,
	booktabs = TRUE,
	digits = 2,
	col.names = c("Ecoregion", "Mean", "SD"),
	caption = "Summary of \\% urban land cover by ecoregion."
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r ISC Land Cover Summary, echo = FALSE}
kable(
	pct.ISC.summary,
	booktabs = TRUE,
	digits = 2,
	col.names = c("Ecoregion", "Mean", "SD"),
	caption = "Summary of \\% impervious surface land cover by ecoregion."
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped"))
```



\newpage
# Network Variable Summaries

Supplemental tables with summaries (i.e., mean and standard deviation) for each variable within the network category.

List of network variables:

+ Site latitude
+ Site longitude
+ Basin area
+ Mean annual flow
+ Mean basin elevation
+ Range basin elevation
+ Site centrality


```{r Numerical Summaries: Network Variables, include = FALSE}
## Latitude
site.lat.summary <- final.DisEQ.data %>%
	select(ecoregion, site.lat) %>%
	group_by(ecoregion) %>%
	summarise(Mean = mean(site.lat), SD = sd(site.lat))

## Longitude
site.long.summary <- final.DisEQ.data %>%
	select(ecoregion, site.long) %>%
	group_by(ecoregion) %>%
	summarise(Mean = mean(site.long), SD = sd(site.long))

## Basin Area
basin.area.summary <- final.DisEQ.data %>%
	select(ecoregion, basin.area) %>%
	group_by(ecoregion) %>%
	summarise(Mean = mean(basin.area), SD = sd(basin.area))

## Mean Annual Flow
mean.annual.flow.summary <- final.DisEQ.data %>%
	select(ecoregion, mean.annual.flow) %>%
	group_by(ecoregion) %>%
	summarise(Mean = mean(mean.annual.flow), SD = sd(mean.annual.flow))

## Mean Basin Elevation
mean.basin.elevation.summary <- final.DisEQ.data %>%
	select(ecoregion, mean.basin.elevation) %>%
	group_by(ecoregion) %>%
	summarise(Mean = mean(mean.basin.elevation), SD = sd(mean.basin.elevation))

## Range Basin Elevation
range.basin.elevation.summary <- final.DisEQ.data %>%
	select(ecoregion, range.basin.elevation) %>%
	group_by(ecoregion) %>%
	summarise(Mean = mean(range.basin.elevation), SD = sd(range.basin.elevation))

## Site Centrality
site.centrality.summary <- final.DisEQ.data %>%
	select(ecoregion, site.centrality) %>%
	group_by(ecoregion) %>%
	summarise(Mean = mean(site.centrality), SD = sd(site.centrality))
```


```{r Latitude Summary, echo = FALSE}
kable(
	site.lat.summary,
	booktabs = TRUE,
	digits = 2,
	col.names = c("Ecoregion", "Mean", "SD"),
	caption = "Summary of latitude by ecoregion."
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r Longitude Summary, echo = FALSE}
kable(
	site.long.summary,
	booktabs = TRUE,
	digits = 2,
	col.names = c("Ecoregion", "Mean", "SD"),
	caption = "Summary of longitude by ecoregion."
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r Basin Area Summary, echo = FALSE}
kable(
	basin.area.summary,
	booktabs = TRUE,
	digits = 2,
	col.names = c("Ecoregion", "Mean", "SD"),
	caption = "Summary of basin area by ecoregion."
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r Mean Annual Flow Summary, echo = FALSE}
kable(
	mean.annual.flow.summary,
	booktabs = TRUE,
	digits = 2,
	col.names = c("Ecoregion", "Mean", "SD"),
	caption = "Summary of mean annual flow by ecoregion."
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r Mean Basin Elevation Summary, echo = FALSE}
kable(
	mean.basin.elevation.summary,
	booktabs = TRUE,
	digits = 2,
	col.names = c("Ecoregion", "Mean", "SD"),
	caption = "Summary of mean basin elevation by ecoregion."
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r Range Basin Elevation Summary, echo = FALSE}
kable(
	range.basin.elevation.summary,
	booktabs = TRUE,
	digits = 2,
	col.names = c("Ecoregion", "Mean", "SD"),
	caption = "Summary of range basin elevation by ecoregion."
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r Site Centrality Summary, echo = FALSE}
kable(
	site.centrality.summary,
	booktabs = TRUE,
	digits = 2,
	col.names = c("Ecoregion", "Mean", "SD"),
	caption = "Summary of site centrality by ecoregion."
	) %>% 
	kable_styling(latex_options = c("HOLD_position", "striped"))
```




